---
title: "Skyline Get daily self efficacy and response efficacy scores"
output:
  html_document:
    df_print: paged
date: '2019-09-12'
---


```{r}
library(tidyverse)
library(here)
```

Preprocessing
==============

Efficacy scores were collected in:
- every 3 days evening questionnaires (!! bug in the plateform, question was presented every day for some participants -> need to work out which and take every 3 day measures)


```{r}
 #get filepaths

#eff_evening_filepath = here("Every3days")

cond_file = "~/Documents/STUDY/EEG-Tobacco/DATA/expe_condition.csv"

save_figure = here("Figures")

#read files

files_eff_eve <-dir(path=here("data") , pattern = "*.csv") 


data_eff <-read.csv(here("data", files_eff_eve), header = TRUE, sep = ",", dec = ".", stringsAsFactors = FALSE)


# condition file
cond <- read_csv(cond_file)


#rename columns 
#- questions scoring: 0 = not at all; 100 = very much

data_eff <-rename(data_eff, date=EndDate, completed=Finished,
                  ID = Q1, 
                  r_eff1 = Q3_1, r_eff2 = Q3_2, 
                  s_eff1= Q4_1, s_eff2 = Q4_2, s_eff3= Q4_3, 
                  hope = Q7_1, 
                  quit_int = Q5
                  )

data_eff$ID<-as.factor(data_eff$ID)


cond <-rename(cond, ID = "Subject ID", condition = "Condition = Intervention", removed= "REMOVED")
cond$ID<-as.factor(cond$ID)

# merge cond and eff files to get information about particopants condition

df <- full_join(cond, data_eff)
df$ID<-as.factor(df$ID)
# remove un-used dataframes
rm(cond, data_eff)

df$condition<-recode(df$condition, '0' = "control", '1' = "intervention")


#Replace missing values and keep only participants who were not removed
df$removed<-df$removed %>% replace(is.na(.), 0)
df<-df%>%filter(removed == 0)

#filter to get only completed = True
df<-df %>%filter(completed == 'True')


```

Do a check of for missing values in the data

```{r}
missing.values <- df %>%
    gather(key = "key", value = "val") %>%
    mutate(is.missing = is.na(val)) %>%
    group_by(key, is.missing) %>%
    summarise(num.missing = n()) %>%
    filter(is.missing==T) %>%
    select(-is.missing) %>%
    arrange(desc(num.missing)) 

```
Look at why we have condition with missing values
```{r}

which(is.na(df$condition))

# remove these lines 

df<-drop_na(df, condition)


```



 Compute response and self efficacy scores
 ------------------------------------------

-> get the mean of all individual scores in each condition for each day
  - 1. define days 1-2-3 etc.. 
  - 2.1 find participants with a maximum of 9 n_day
  - 2.2 find participants with more than 9 n_day entries
    2.3-> take only only every 3 days: 1, 6, 9, 12, 15, 18, 21
  -> create new dataset  
  - 3. count how many of each day per condition



```{r}
# first reduce number of columns to keep only those of interest
df <- select(df, ID, condition, date, r_eff1:quit_int )

# transform the columns for response and self efficacy that were charactuers in numeric tyoe           
df <-df %>% mutate_each(funs(as.numeric), -ID, -quit_int, -date, -condition) 

# add a counter for each row per ID (see 1.)
df <- df %>% 
  group_by(ID) %>% 
  mutate(n_day = row_number()) %>% 
  select(ID, condition, n_day, everything())

df$n_day<-as.factor(df$n_day)
df$condition <- as.factor(df$condition)

# get IDs of pp who did the survey every day instead of every 3 days
get_ID_bug <- df %>% 
  group_by(ID) %>% 
  mutate(count = row_number()) %>% 
  filter(count>9) %>% 
  distinct(ID)
  
# for those IDs, only select data from the 1, 6, 9, 12, 15, 18, 21, 24, 27 days, and rename 1:9   

days<-c(1, 6, 9, 12, 15, 18, 21, 24, 27)


# create a new dataframe combining all pps 
df9<- df %>% 
  filter(ID %in%get_ID_bug$ID & n_day %in% days) 
  
df9$n_day<-recode_factor(df9$n_day, '1' = "1", '6'="2", '9'="3", '12' ="4", '15'="5", '18'="6", '21'="7", '24'="8", '27'="9")

tmp <- df %>% 
  filter(! ID %in% (get_ID_bug$ID) )

df9<- rbind(df9, tmp)


# count how many of each day per condition
# _> need to get summary per condition per day not repetitionShow in New WindowClear OutputExpand/Collapse Output

n_rep <- df9 %>% group_by(condition, n_day) %>%
 summarize(count=n())

n_rep <-n_rep %>% drop_na()

# plot
ggplot(data= n_rep, aes(x = n_day, y=count)) +
  geom_point(mapping = aes(colour = condition) ) +
  ggtitle("Number of response per day - efficacy questionnaire")

  ggsave('nresp_per_day.jpg', plot =last_plot(), dpi =300, path= save_figure)

 


```

- 3. Compute mean response and self efficacy score for each day for each pp

- 4. plot
!!! different number of data points per paricipant !!!



```{r}
# compute total score for each measure for each day and each participant

df9 <- df9 %>% group_by(ID, n_day) %>% 
  mutate(total_re= sum(r_eff1, r_eff2), 
         total_se= sum(s_eff1, s_eff2, s_eff3)
         )


# compute mean totol of response and self efficacy score for each day for each condition
m_scores <- df9 %>% group_by(condition, n_day) %>% 
  summarize(mean_re= mean(total_re,na.rm=TRUE), 
            mean_se=mean(total_se, na.rm=TRUE), 
            mean_hope = mean(hope, na.rm=TRUE))

m_scores <- left_join(m_scores, n_rep)

# plot on 2 different graph response efficacy and self efficacy
m_scores %>% gather("type", "score", 3:4 ) %>% 
  ggplot(data=., mapping=aes(x= n_day, y=score)) +
         geom_point(mapping = aes(colour=condition, size=count), alpha=1/3)+
        facet_wrap(~type)+
  geom_smooth(se=FALSE)+
  ggtitle("Mean scores for response and self efficacy per day per condition")
  
  ggsave('efficacy_scores.jpg', plot =last_plot(), dpi =300, path= save_figure)



```


```{r}

# plot hope

ggplot(data=m_scores, mapping=aes(x= n_day, y=mean_hope)) +
       geom_point(mapping = aes(colour=condition, size=count), alpha=1/3)+
      geom_smooth(se=FALSE)+
ggtitle("Mean scores for how hopeful about quitting smoking")

  ggsave('hope_scores.jpg', plot =last_plot(), dpi =300, path= save_figure)


```


Next step: model










