---
title: "Skyline Get daily self efficacy and response efficacy scores"
output: html_notebook
date: 2019-09-12
---


```{r}
library(tidyverse)
library(lubridate)
```

Preprocessing
=====================================================

Efficacy scores were collected in:
- every 3 days evening questionnaires (!! bug in the plateform, question was presented every day for some participants -> need to work out which and take every 3 day measures)


```{r}
 #get filepaths

eff_evening_filepath = "~/Documents/STUDY/EEG-Tobacco/DATA/SURVEYS/Every3days"

cond_file = "~/Documents/STUDY/EEG-Tobacco/DATA/expe_condition.csv"


output_filepath = "~/Documents/STUDY/EEG-Tobacco/DATA/SURVEYS"

#read files

files_eff_eve <-dir(path= eff_evening_filepath, pattern = "*.csv") 

data_eff <-read.csv(file.path(eff_evening_filepath, files_eff_eve), header = TRUE, sep = ",", dec = ".", stringsAsFactors = FALSE)

# condition file
cond <- read_csv(cond_file)


#rename columns 
#- questions scoring: 0 = not at all; 100 = very much

data_eff <-rename(data_eff, date=EndDate, completed=Finished,
                  ID = Q1, 
                  r_eff1 = Q3_1, r_eff2 = Q3_2, 
                  s_eff1= Q4_1, s_eff2 = Q4_2, s_eff3= Q4_3, 
                  hope = Q7_1, 
                  quit_int = Q5
                  )

data_eff$ID<-as.factor(data_eff$ID)


cond <-rename(cond, ID = "Subject ID", condition = "Condition = Intervention", removed= "REMOVED")
cond$ID<-as.factor(cond$ID)

# merge cond and eff files to get information about particopants condition

df <- full_join(cond, data_eff)
df$ID<-as.factor(df$ID)
# remove un-used dataframes
rm(cond, data_eff)


#Replace missing values and keep only participants who were not removed
df$removed<-df$removed %>% replace(is.na(.), 0)
df<-df%>%filter(removed == 0)

#filter to get only completed = True
df<-df %>%filter(completed == 'True')


```

 Compute response and self efficacy scores
 ------------------------------------------


```{r}
# first reduce number of columns to keep only thoe of interest
df_sml <- select(df, ID, condition, date, r_eff1:quit_int )

df_sml<-df_sml %>% mutate_each(funs(as.numeric), -ID, -quit_int, -date) 

 mutate(df_sml, 
       RE_score = ave(df_sml$r_eff1, df_sml$r_eff2))

df_sml<- df_sml %>%
  group_by(ID) %>%
  mutate(df_sml, 
       RE_score = ave(df_sml$r_eff1, df_sml$r_eff2))
```





Arrange data by participants'ID 

```{r}

data_eff_tmp<- data_eff %>%  group_by(ID) 
%>%
  tally()
  
data_eff_tmp <- rename(data_eff_tmp, ev3days = n)
```







Get the difference between participant enrolled (= have a participant ID) and those who actually conpleted at least 1 survey

```{r}
# for data_day
test<-anti_join(cond, data_eff)
```




3. Collate data from all day and evening survey within the same dataframe

+ make sure we only look at data from real participant by taking only the IDs present on the condition file

```{r}
sum_data<- inner_join(cond, data_day_tmp, by = 'ID', copy=TRUE )
sum_data<-left_join(data_day_tmp,data_eve_tmp, by = 'ID', copy=TRUE)
sum_data<-left_join(sum_data, data_eff_tmp, by = 'ID', copy=TRUE)

## add information from condition file
sum_data<-left_join(sum_data, cond, by = 'ID', copy=TRUE)

# get only real participant in followup datasets

sum_data_followup <- inner_join(cond, data_followup, by = 'ID', copy=TRUE )

sum_data_followup_lab <- inner_join(cond, data_followup_lab, by = 'ID', copy=TRUE )


```



4. Overview of performance

Number of participants who completed 80% of daily surveys:

```{r}
sum(sum_data$day_msg >66)
```

Number of participants who completed between 50% and 80% of daily surveys:

```{r}
sum(sum_data$day_msg %in% 41:66)

```

Number of participants who completed less than 50% of daily surveys:

```{r}
sum(sum_data$day_msg %in% 1:40)
```

Number of participants who completed online follow up questionnaire:

```{r}
sum(sum_data_followup$completed == 'True')

```

Number of participants who completed lab based follow up questionnaire:
```{r}
sum(sum_data_followup_lab$completed == 'True')

```


Number of participants who dropped out from the start (ie. never completed an online survey):

```{r}
nrow(dropout)
```
















