---
title: "Skyline Survey data analysis Response to smoking health warnings at baseline and follow up "
output: html_notebook
---

Process both EEG and online data


```{r}
library(tidyverse)
library(here)
library(lubridate)


fpath = here::here("data")
cond_file = "~/Documents/STUDY/EEG-Tobacco/DATA/expe_condition.csv"
save_figure = here::here("Figures")

#read files

files <-dir(path=here::here("data"), pattern = "*.csv") 

#'read in qualtrics data while skipping qualtrics column names row to have access directly to question text as column name
data_smok_resp <- files %>% 
      map(~read_csv(file.path(fpath, .), col_names = TRUE, skip =0)) %>% 
      reduce(bind_rows)  


# condition file
cond <- read_csv(cond_file)

cond<-rename(cond,  ID = "Subject ID", condition = "Condition = Intervention", removed= "REMOVED")

cond$ID<-as.factor(cond$ID)



```

Rename columns

Neg_disgust = Q10_1, Q19_1, Q25_1, Q31_1, Q37_1, Q43_1
Neg_scared = Q10_2, Q19_2, Q25_2, Q31_2, Q37_2, Q43_2
Neg_regret = Q10_3, Q19_3, Q25_3, Q31_3, Q37_3, Q43_3
Believe = Q13_1, Q20_1, Q26_1, Q32_1, Q38_1, Q44_1
Harm = Q13_2, Q20_2, Q26_2, Q32_2, Q38_2, Q44_2
Effect_discourage=Q13_3, Q20_3, Q26_3, Q32_2, Q38_3, Q44_3 
Effect_unpleasant= Q13_4, Q20_4, Q26_4, Q32_4, Q38_4, Q44_4
Effect_concern = Q13_5, Q20_5, Q26_5, Q32_5, Q38_5, Q44_5
React_manip = Q14_1, Q21_1, Q22_1, Q33_1, Q39_1, Q45_1  
React_overblow = Q14_2, Q21_2, Q27_2, Q33_2, Q39_2, Q45_2
React_annoy = Q14_3, Q21_3, Q27_3, Q33_3, Q39_3, Q45_3
Avoid_think= Q15_1, Q22_1, Q28_1, Q34_1, Q40_1, Q46_1 
Avoid_look = Q15_2, Q22_2, Q28_2, Q34_2, Q40_2, Q46_2
Avoid_sight = Q15_3, Q22_3, Q28_3, Q34_3, Q40_3, Q46_3



Find a way to sum data of columns for same question  by selecting based on word in question 
ex: select(data_smok_resp, contains("avoid thinking"))




```{r}

data_smok_resp <-rename(data_smok_resp, ID = Q1)
data_smok_resp$ID<-as.factor(data_smok_resp$ID)
               

# transform the columns  that were charactuers in numeric tyoe           
data_smok_resp <-data_smok_resp %>% mutate_each(funs(as.numeric), -ID, -Q3, -EndDate, -Finished) 




tmp <- data_smok_resp %>% 
  group_by(ID) %>% 
  transmute(
        date=EndDate, 
        completed=Finished,
        Quit_int = Q3, 
        Like_harm = Q4_1,
        Severity_harm = Q7_1,
        Neg_disgust = sum(Q10_1, Q19_1, Q25_1, Q31_1, Q37_1, Q43_1), 
        Neg_scared = sum(Q10_2, Q19_2, Q25_2, Q31_2, Q37_2, Q43_2), 
        Neg_regret = sum(Q10_3, Q19_3, Q25_3, Q31_3, Q37_3, Q43_3), 
        Believe = sum(Q13_1, Q20_1, Q26_1, Q32_1, Q38_1, Q44_1), 
        Harm = sum(Q13_2, Q20_2, Q26_2, Q32_2, Q38_2, Q44_2), 
        Effect_discourage= sum(Q13_3, Q20_3, Q26_3, Q32_2, Q38_3, Q44_3),  
        Effect_unpleasant= sum(Q13_4, Q20_4, Q26_4, Q32_4, Q38_4, Q44_4), 
        Effect_concern = sum(Q13_5, Q20_5, Q26_5, Q32_5, Q38_5, Q44_5), 
        React_manip = sum(Q14_1, Q21_1, Q22_1, Q33_1, Q39_1, Q45_1),  
        React_overblow = sum(Q14_2, Q21_2, Q27_2, Q33_2, Q39_2, Q45_2),
        React_annoy = sum(Q14_3, Q21_3, Q27_3, Q33_3, Q39_3, Q45_3),
        Avoid_think= sum(Q15_1, Q22_1, Q28_1, Q34_1, Q40_1, Q46_1), 
        Avoid_look = sum(Q15_2, Q22_2, Q28_2, Q34_2, Q40_2, Q46_2),
        Avoid_sight = sum(Q15_3, Q22_3, Q28_3, Q34_3, Q40_3, Q46_3)
         )

df<- full_join(cond, tmp)

df$ID <- as.factor(df$ID)

rm(cond, tmp, data_smok_resp)

df$condition<-recode(df$condition, '0' = "control", '1' = "intervention")
df$condition <- as.factor(df$condition)

#Replace missing values and keep only participants who were not removed
df$removed<-df$removed %>% replace(is.na(.), 0)
df<-df%>%filter(removed == 0)

#filter to get only completed = True
df<-df %>%filter(completed == 'True')

```




Do a check of for missing values in the data

```{r}

missing.values <- df %>%
    gather(key = "key", value = "val") %>%
    mutate(is.missing = is.na(val)) %>%
    group_by(key, is.missing) %>%
    summarise(num.missing = n()) %>%
    filter(is.missing==T) %>%
    select(-is.missing) %>%
    arrange(desc(num.missing)) 

missing.values
```

Look at why we have condition with missing values
```{r}

which(is.na(df$condition))

# remove these lines 

df<-drop_na(df, condition)


```


```{r}

df_tmp<- df %>% 
  group_by(ID) %>% 
  tally()



```



